Image Processing for Discovering\\ the Rules of Video Games

### 2018-04-18 proposal/paper.tex
Added pictures

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{graphicx}
\graphicspath{ {images/} }

@@

@@

Another solution would be to allow the algorithm to learn for a longer period of time. The NEAT algorithm ran for 121 generations with a population of 150. Over the 121 generations the best performing networks max fitness hovered around 39 out of 177 never showing improvement from generation to generation. As you can see from {FIGURE REF HERE} over generation 111 to 121 there is no improvement in the fitness. Given more time for the algorithm to build a bigger graph or reducing the input we believe that the algorithm would be able to improve its fitness.
Another problem with our algorithm is that it took a very long time to learn. It took roughly 6 days to learn 121 generations. There are a couple of ways we think we can improve this time. The easiest being to introduce a timeout function that will fail the network after a set number of frames that have not added to the fitness of the network.

>>>>

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{caption}
\usepackage{subcaption}

@@

For the NEAT algorithm are input was the image of the screen. Are image was 256x224 colored image which ment that we had to have 172,032 inputs to be able to hand the size of the image and the 3 RGB values per pixel. This was way to large for the NEAT alogrithm to handle to to reduce it we pixelated the image into a 28x32 image as shown in figure 1-4. By doing this we were able to reduce are input to 2,688 still taking into account the RGB values of each pixel. Are outputs to are neural network were the 4 inputs the game accepted Up, Down, Left, and Right.

\begin{figure}
\centering
\begin{minipage}{.25\textwidth}
  \centering
  \includegraphics[width=.95\linewidth]{Original1.png}
  \captionof{figure}{Original}
  \label{fig:test1}
\end{minipage}%
\begin{minipage}{.25\textwidth}
  \centering
  \includegraphics[width=.95\linewidth]{pixel1.png}
  \captionof{figure}{Pixelated}
  \label{fig:test2}
\end{minipage}
\end{figure}
\begin{figure}
\centering
\begin{minipage}{.25\textwidth}
  \centering
  \includegraphics[width=.95\linewidth]{Original2.png}
  \captionof{figure}{Original}
  \label{fig:test1}
\end{minipage}%
\begin{minipage}{.25\textwidth}
  \centering
  \includegraphics[width=.95\linewidth]{pixel2.png}
  \captionof{figure}{Pixelated}
  \label{fig:test2}
\end{minipage}
\end{figure}

@@

Another solution would be to allow the algorithm to learn for a longer period of time. The NEAT algorithm ran for 121 generations with a population of 150. Over the 121 generations the best performing networks max fitness hovered around 39 points out of the total 177 points and did not show much improvement from generation to generation as shown in figure 5. Given more time for the algorithm to build a bigger graph or reducing the input we believe that the algorithm would be able to improve its fitness.

\begin{figure}
\centering
  \includegraphics[width=1\linewidth]{avg_fitness.png}
\end{figure}

Another problem with our algorithm is that it took a very long time to learn. It took roughly 6 days to learn 121 generations. There are a couple of ways we think we can improve this time. The easiest being to introduce a timeout function that will fail the network after a set number of frames that have not added to the fitness of the network.
